---
title: "Prop 11"
author: "Jared Joseph & Savannah Hunter"
date: "October 30, 2018"
output:
  ioslides_presentation: 
    fig_caption: yes
    widescreen: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Prop 11 {.smaller}

<div class="columns-2">

* Requires Private-Sector Emergency Ambulance Employees to Remain on Call During Work Breaks.

  + Employers will provide paid training on active shooter and mass casualty incidents, natural disasters, preventing violence to themselves and patients (some already receive training).

+ Requires employers to provide mental health and wellness education with 30 days of hire and each year.

+ Requires employers to make information about mental health treatment and support services known (some already have this benefit).

+ Requires employers to provide coverage of up to 10 mental health treatments per year. Qualified employees can receive long-term services.

```{r}
table = data.frame(Yes = c("Private ambulance companies can continue their current practice (illegal under current labor law) of having EMTs and paramedics to stay on-duty “on call” during their meal and rest breaks to answer 911 calls. If scheduled breaks are interrupted by a call that meal or rest period does not count toward the meal or rest period entitled to the employee.
", "$29,925,785.96 (most by American Medical Response one of the largest private EMT and paramedic employers)",  "Any pending lawsuits for violating past labor law may be prevented.  "),
No = c("Private companies will be subject to labor law. Based on a 2016 court case these companies would have to provide EMTs and paramedics with off-duty meal and rest breaks that cannot be interrupted by 911 calls.", "$0.00", "Ambulance company costs may increase by about $100 million a year to operate more ambulances to fill in during breaks.")
#row.names = c("Basics", "Funding", "Impact")
)

knitr::kable(table)
```

</div>

***



```{r plot, echo=FALSE}

```

